Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-10-09 awipev-CO2.Rmd

### **REMOS**
- **2019-09-07**: REMOS back in the water.
- **2019-09-02**: REMOS removed from the water for maintenance with Philipp and Samir.
- **2018-11-24**: REMOS stopped because of an iceberg. At the moment we dont know if instruments are still there/broken.

### **FerryBox**
- **2020-01-24**: heater issues in the contenair (power shutdown maybe) caused some samples to freeze. See part "SNAPO" for details on samples.
- **2019-09-01**: Some interruptions for the FB during 2 weeks of maintenance.
- **2019-06-12**: Markus came to do maintenace. 
- **2019-06-05**: Problem in the relay 15 that controls the waste water pump was found. The spare part will be brought here next week (when Samir will leave...).
- **2019-06-03**: Samir is on site alone. Different tests were made. Maybe the 2 tapes that feed TA and pCO2 are responsible of the problem (low flow).
- **2019-05-22**: FB is stopped because of several problems. Philipp and Marine are working on it.
- **2019-05-21**: FB is unstable. 
- **2019-04-14**: FB is working again. 
- **2019-04-13**: FB is stopped since 05:00am (the level switch stuck in the full position in the waste tank). 
- **2019-02-27**: FB is working again. 
- **2019-02-26**: FB is stopped because of a "leakage" issue. 
- **2019-01-17**: FB is stopped until 19th January 
- **2019-01-11**: FB is stopped until 12th Decmeber. 
- **2018-12-28**: FB is stopped until 31st Decmeber. 
- **2018-10-12**: FB is working again. 
- **2018-10-10**: FB is stopped after a seawater leakage. 
- **2018-10-08**: FB is working again. 
- **2018-10-05**: FB is stopped after a seawater leakage. 
- **2018-09-12**: FB is stopped. Problems inland could be the reason. The same day Marine make it working again.
- **2018-04-14**: FB is working again. They made an outlet "by-pass" tube to flush the seawater directly on the beach, not at 11 m.
- **2018-03-08**: Last data at 23:59. Frozen Ferrybox system (outlet tubings) in Svalbard, maybe due to a power failure over night in Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
- **2017-05-24**: FerryBox was shut down due to many connexion issues...see Philipp's email 24/05/2017 18:17.
- **2017-03-20**: Philipp arrived in NYA to solve the problem.
- **2017-03-11**: Iceberg destroyed the power-pumps cables (Philipp's email on 2017-03-11 10:40). No more data for all parameters.
- **2017-01-31**: Beginning of the 14-days FB maintenance by Philipp and Uwe. Gaps in data could be present during this period.
- **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17 21:00 to 2017-01-19.
- **2016-09-24**: No data because of maintenance until the 28th. Except for TA wich has data available for this period.
- **2016-09-20**: Test in the Ferrybox with the seawater. Seawater was "sucked" (not pumped) from 7:40 to 10:00 by a vaccum system in order to test it. This system was installed if the pumps 1 and 2 broke during winter. This is a "plan C". This system is not automatic and we will be informed about its power up in case of emergency. As long as the water is not pumped with this system, we have to monitor the data because changements in gas partial pressure can occur.
- **2016-09-12**: No data because of maintenance until the 18th.
- **2016-09-10**: No data because of maintenance until the 11th.
- **2016-05-09**: data are back.
- **2016-05-04**: No data for all parameters because of electricity issues. 
- **2016-04-23**: FerryBox was shut down by AWI team for maintenance.
- **2016-02-23**: FerryBox was switched on by AWI team after maintenance.
- **2015-12-20**: FerryBox was shut down because of pump issues. Waiting for the maintenance in February.
- **2015-11-27**: The ferrybox was down from Nov. 18th until today Nov. 27th. (emails from P.Fischer 2015-11-24 23:09 and Station Leader AWIPEV 2015-11-27 12:57). Tubes frozen.

>>>>

### **REMOS**
- **2020-09-23**: REMOS started at 20:00 UTC.
- **2020-09-22**: REMOS stopped at 19:00 UTC because of a power shutdown.
- **2019-03-12**: REMOS on.
- **2020-02-24**: REMOS off.
- **2019-09-07**: REMOS back in the water.
- **2019-09-02**: REMOS removed from the water for maintenance with Philipp and Samir.
- **2018-11-24**: REMOS stopped because of an iceberg. At the moment we dont know if instruments are still there/broken.

### **FerryBox**
- **2020-09-30**: FB started at 19:00 UTC.
- **2020-09-29**: FB stopped at in the morning for few hours.
- **2020-09-26**: FB stopped at in the morning for few hours.
- **2020-09-25**: FB stopped at in the morning for few hours.
- **2020-09-23**: FB started at 20:00 UTC.
- **2020-09-22**: FB stopped at 19:00 UTC because of a power shutdown.
- **2020-09-22**: FB started again at 08:00 UTC after several months of locked down. Lisa repaired it in few minutes only. 
- **2020-09-22**: FB started again after several months of locked down. Lisa repaired it in few minutes only. 
- **2020-07-25**: FB stopped. Not possible to go inside to repair because the FB is locked after the "mercurygate". IPEV locked the FB with suspicion of mercury contamination rose up by Bettina (Stationleader)
- **2020-05-24**: FB started again after several months of on activity due to very cold T and frozen pipes.
- **2020-02-18**: FB stopped because of frozen pipes.
- **2020-01-24**: heater issues in the contenair (power shutdown maybe) caused some samples to freeze. See part "SNAPO" for details on samples.
- **2019-09-01**: Some interruptions for the FB during 2 weeks of maintenance.
- **2019-06-12**: Markus came to do maintenace. 
- **2019-06-05**: Problem in the relay 15 that controls the waste water pump was found. The spare part will be brought here next week (when Samir will leave...).
- **2019-06-03**: Samir is on site alone. Different tests were made. Maybe the 2 tapes that feed TA and pCO2 are responsible of the problem (low flow).
- **2019-05-22**: FB is stopped because of several problems. Philipp and Marine are working on it.
- **2019-05-21**: FB is unstable. 
- **2019-04-14**: FB is working again. 
- **2019-04-13**: FB is stopped since 05:00am (the level switch stuck in the full position in the waste tank). 
- **2019-02-27**: FB is working again. 
- **2019-02-26**: FB is stopped because of a "leakage" issue. 
- **2019-01-17**: FB is stopped until 19th January 
- **2019-01-11**: FB is stopped until 12th Decmeber. 
- **2018-12-28**: FB is stopped until 31st Decmeber. 
- **2018-10-12**: FB is working again. 
- **2018-10-10**: FB is stopped after a seawater leakage. 
- **2018-10-08**: FB is working again. 
- **2018-10-05**: FB is stopped after a seawater leakage. 
- **2018-09-12**: FB is stopped. Problems inland could be the reason. The same day Marine make it working again.
- **2018-04-14**: FB is working again. They made an outlet "by-pass" tube to flush the seawater directly on the beach, not at 11 m.
- **2018-03-08**: Last data at 23:59. Frozen Ferrybox system (outlet tubings) in Svalbard, maybe due to a power failure over night in Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
- **2017-05-24**: FerryBox was shut down due to many connexion issues...see Philipp's email 24/05/2017 18:17.
- **2017-03-20**: Philipp arrived in NYA to solve the problem.
- **2017-03-11**: Iceberg destroyed the power-pumps cables (Philipp's email on 2017-03-11 10:40). No more data for all parameters.
- **2017-01-31**: Beginning of the 14-days FB maintenance by Philipp and Uwe. Gaps in data could be present during this period.
- **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17 21:00 to 2017-01-19.
- **2016-09-24**: No data because of maintenance until the 28th. Except for TA wich has data available for this period.
- **2016-09-20**: Test in the Ferrybox with the seawater. Seawater was "sucked" (not pumped) from 7:40 to 10:00 by a vaccum system in order to test it. This system was installed if the pumps 1 and 2 broke during winter. This is a "plan C". This system is not automatic and we will be informed about its power up in case of emergency. As long as the water is not pumped with this system, we have to monitor the data because changements in gas partial pressure can occur.
- **2016-09-12**: No data because of maintenance until the 18th.
- **2016-09-10**: No data because of maintenance until the 11th.
- **2016-05-09**: data are back.
- **2016-05-04**: No data for all parameters because of electricity issues. 
- **2016-04-23**: FerryBox was shut down by AWI team for maintenance.
- **2016-02-23**: FerryBox was switched on by AWI team after maintenance.
- **2015-12-20**: FerryBox was shut down because of pump issues. Waiting for the maintenance in February.
- **2015-11-27**: The ferrybox was down from Nov. 18th until today Nov. 27th. (emails from P.Fischer 2015-11-24 23:09 and Station Leader AWIPEV 2015-11-27 12:57). Tubes frozen.
